Staged Abstract Interpreters

### 2019-08-31 paper/60_cases.tex
typo

As we have already seen from Section \ref{sai}, and recall the
primitive operation \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{close} that denotes a $\lambda$ term to next-stage
Scala function.  The specializing of staged abstract interpreter to
$\lambda$ terms is independent to other parts of the analyzed program.
\begin{lstlisting}
  def close(ev: Eval => Ans)(λ: Expr, ρ: Rep[Env]): Rep[Value]
\end{lstlisting}

>>>>

As we have already seen from Section \ref{sai}, and recall that the
primitive operation \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{close} can denote a $\lambda$ term to a next-stage Scala function.  The specializing of the staged abstract interpreter to
$\lambda$ terms is independent to other parts of the analyzed program.
\begin{lstlisting}
  def close(ev: Eval => Ans)(λ: Expr, ρ: Rep[Env]): Rep[Value]
\end{lstlisting}
